Greedy Heuristics for Solving the Weighted Orthogonal Art Gallery Problem

### 2020-09-02 doc/paper.tex
new ideas for g-function included

       The best WSC problem greedy heuristic known from the literature was based on the following greedy heuristic:
       \begin{align}
          g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
       \end{align} 
      where $f(s^p) = |\bigcup_{s \in s^p} s |$.
        \subsection{An Alternative Greedy Heuristic}
        \fxnote{TODO: work in progress...} Greedy criterion:
          \begin{itemize}
          	\item prefer those guards with a smaller cost $w_i$;
          	\item If there are more guards with the smallest cost,
          	prefer one with the largest $S_{p_i}$.
          \end{itemize}
		\fxnote{TODO: work in progress...} Another approach DRAGAN:
           \begin{itemize}
			\item introduce a penalty function
          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
			\item let $w_{total}$ be the total sum of all weights among all verteces
			\item involve the penalty function in the objective function
				$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
				$$obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}$$\fxnote{moguce i skaliranje ove dvije vrijednosti?}
			\item start Greedy with empty solution
			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
			\item end when $incorrect_{total}$ becomes 0
          \end{itemize}
      \subsection{An improvement of Greedy Solution}
      Local search and Large Neighborhood search \fxnote{TODO...}
      Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
      The first configuration of neighbourhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t. value $obj(;)$.

>>>>

       The best WSC problem greedy heuristic known from the literature was based on the following greedy heuristic:
       \begin{align}
          g(s^p, p_i) = \frac{w_{p_i}}{ f(s^p \cup \{p_i\})  - f(s^p)},
       \end{align} 
      where $f(s^p) = |\bigcup_{s \in s^p} s |$.

      One additional criterion can be given as a measure of intersection between one set  $S_{p_i}$ and 
      and the other sets $S_{p_j}$, $j \neq i$ as follow:
      \begin{align}\label{eq:intersection-heuristic}
      	   g(s^P,p_i) = \frac{\sum_{p_j \in V \setminus s^P: p_i \neq p_j}|S_{p_i} \cap S_{p_j}|}{|V|-|s^P|-1}, p_i \in V \setminus s^P,
      \end{align}
      where $|S_{p_i} \cap S_{p_j}|$ denotes the surface (in some unit) of the intersection of the two 
      visible regions. If some set $S_{p_i}$ has less intersection with the  visible regions of other candidate guards it is more likely that $p_i$ will be a good candidate for a guard. So, based on it, we try to always add a vertex $p_j$ to $s^P$ which has the smallest $g$ value acc. to formula~(\ref{eq:intersection-heuristic})

        \subsection{An Alternative Greedy Heuristic}
        \fxnote{TODO: work in progress...} Greedy criterion:
          \begin{itemize}
          	\item prefer those guards with a smaller cost $w_i$;
          	\item If there are more guards with the smallest cost,
          	prefer one with the largest $S_{p_i}$.
          \end{itemize}
		\fxnote{TODO: work in progress...} Another approach DRAGAN:
           \begin{itemize}
			\item introduce a penalty function
          	\item introduce a term ``incorrect point''. For a point from D(P) we say that it is incorrect if it is not covered by any guard from a current partial solution $s^{ps}$.
			\item let $incorrect_{total}$ be the total number of incorrect points from discretisazion $D(P)$
			\item let $w_{total}$ be the total sum of all weights among all verteces
			\item involve the penalty function in the objective function
				$$obj(s^{ps}; v)  = \sum_{i \in s^{ps} \cup \{v\}} w_i+ incorrect_{total}$$ or
				$$obj(s^{ps}; v) = \frac{\sum_{i \in s^{ps} \cup \{v\}\}} w_i}{w_{total}}+ \frac{incorrect_{total}}{|D(P)|}$$\fxnote{moguce i skaliranje ove dvije vrijednosti?}
			\item start Greedy with empty solution
			\item in each iteration add such a guard to $s^{ps}$ for which the obj value is minimal
			\item end when $incorrect_{total}$ becomes 0
          \end{itemize}
      \subsection{An improvement of Greedy Solution}
      Local search and Large Neighborhood search \fxnote{TODO...}
      Local search (LS) technique is a basis of the LS--based metaheuristics. Let us define the structure of neighborhood. We define them over the set of guards.
      The first configuration of neighbourhood of some partial solution is operation of swapping; that means from a given partial solution $s^P$, we choose one guard from $s^P$ and then pick another guard from $V \setminus s^p$ w.r.t. value $obj(;)$.
